Hyperopt-Sklearn: Subtitle?

### 2014-04-26 papers/2014-automl/paper.tex
paper merge fig3 and fig4

\begin{figure}
    \centering
    \includegraphics[width=4.5in]{graphics/scores_by_classifier}
    %\includegraphics[width=2.9in]{graphics/scores_per_eval}
    \caption{
	    Using Hyperopt's Anneal search algorithm, increasing the number of function evaluations from 150 to 2400 lead to a modest improvement in accuracy on 20 Newsgroups and MNIST,
        and a more dramatic improvement on Convex Shapes.
        We capped evaluations to 5 minutes each so 300 evaluations took between 12 and 24 hours of wall time.
    }
    \label{fig:per_clf}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=3in]{graphics/AvgMinValidErrorTPE}
    \caption{
        Hyperopt's TPE algorithm makes gradual progress on 20 Newsgroups over 300 iterations and gives no indication of convergence.
        We look forward to investigating alternative optimization algorithms in future work.
    }
    \label{fig:errtpe}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=3.0in]{graphics/scores_by_classifier}
    \includegraphics[width=2.8in]{graphics/AvgMinValidErrorTPE}
    %\includegraphics[width=2.9in]{graphics/scores_per_eval}
    \caption{
	    Left: Using Hyperopt's Anneal search algorithm, increasing the number of function evaluations from 150 to 2400 lead to a modest improvement in accuracy on 20 Newsgroups and MNIST,
        and a more dramatic improvement on Convex Shapes.
        We capped evaluations to 5 minutes each so 300 evaluations took between 12 and 24 hours of wall time.
        Right: TPE makes gradual progress on 20 Newsgroups over 300 iterations and gives no indication of convergence.
    }
    \label{fig:per_clf}
\end{figure}

\begin{figure}
    \centering
    \caption{
    }
    \label{fig:errtpe}
\end{figure}
